#Housing Prices Exploration 
#by Derek Stratton

========================================================

###Abstract

My fiance and I are getting married next month and we're in the process of
searching for a new home for our future family. There are many factors to 
consider when purchasing a new home, a few of them being: price, location, 
future value, school districts, and safety. Although this data does not pertain
to the city in which we are house hunting, the exploration process should
provide valuable insight into what factors have the biggest influence on the
price of a home.

###Resources

Downloaded dataset from: https://www.kaggle.com/harlfoxem/housesalesprediction

This dataset contains house sale prices in King County, Washington between
May 2014 to May 2015. 

Other resources used:

http://ggplot2.tidyverse.org/reference/

http://bbs.ceb-institute.org/wp-content/uploads/2011/09/handout_ggplot2.pdf

http://www.cookbook-r.com/Graphs/Bar_and_line_graphs_(ggplot2)/

https://s3.amazonaws.com/udacity-hosted-downloads/ud651/
GeographyOfAmericanMusic.html

https://s3.amazonaws.com/content.udacity-data.com/courses/ud651/
diamondsExample_2016-05.html

https://s3.amazonaws.com/udacity-hosted-downloads/ud651/
AtlanticHurricaneTracking.html

https://github.com/Shreyas3108/house-price-prediction/blob/master/
housesales.ipynb

https://www.rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf

http://www.sthda.com/english/wiki/ggplot2-scatter-plots-quick-start-guide
-r-software-and-data-visualization



###Dataset Preparations
library(ggplot2)
library(knitr)
library(dplyr)
library(maps)
options(scipen=999)

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
library(ggplot2)
library(knitr)
library(dplyr)
library(maps)
options(scipen=999)
```

```{r echo=FALSE, Load_the_Data}
setwd('C:/Users/National Positions/Anaconda2/Section 6 - Exploratory Data Analysis/project')

houses_data <- read.csv('kc_house_data_small.csv')
```

## Univariate Plots Section

```{r}
names(houses_data)

```

###Variable Observations & Analysis:

There are a total of 21 variables within the dataset. The "yr_built" variable
is nice to know because buying an older home, although sometimes less
expensive than alternatives, may unearth unwanted repairs and remodeling, 
resulting in more money spent and more stress as a new homeowner. I also will
be creating an "age" variable based on the "yr_built" because it will be easier
to understand. 

Location is a strong factor for us so the "zipcode", "lat", and "long" 
variables are very interesting to me. I'd like to explore ways of using these
values within a plot to visually see where the most and least expensive homes
are located. 

Overall, all of the variables are of interest me. 

```{r}
str(houses_data)

```

###Structure Observations & Analysis:

The structure of this dataset is a data frame and consists of 21 total 
variables, including 3 different data types: numeric, integer, 
and Factor. I already envisioned creating grouped distrbution graphs so I will
be converting a few variables into Factors, such as "bedrooms". 

```{r}
summary(houses_data)

```

###Summary Observations & Analysis:

The first thing I wanted to try and identify using the summary was any 
outliers. Right off the bat I noticed the dataset contained records where there
were values of zero for "bedrooms". I definitely want to omit those before 
analyzing further. I also need to be mindful of what summary statistic is more
appropriate to use - mean or median? Depending on my objective, there will be 
instances when the median is a better fit, especially if there are few records
being compared. 

### Initial Exploration

I discovered there were instances where homes had zero bedrooms. This sounds 
implausible and was probably due to input error, but at any rate, I want to 
remove these records.

```{r}
#find all instances when bedrooms is equal to zero
count(houses_data, bedrooms==0)

```

It looks like there is only one home that contains zero bedrooms. I will now
create a subset of the dataset that omits this instance.

```{r}
# remove all instances when bedrooms is equal to zero
homes <- subset(houses_data, bedrooms > 0)

```

The resulting dataframe has 2999 objects, which is the expected number since
our original dataset contained 3000 objects and we were only omitting 1.

Now I want to convert the "yr_built" values into "age" because I think it's an
easier way to understand how old a home actually is.

```{r}
#add an "age" column by subtrating the yr_built from 2018
homes$age <- 2018 - homes$yr_built

```

Our new "homes" dataset now has a new numeric data-type variable called "age".

Next, I will create a new "bedrooms" variable that is of Factor data-type 
because I will need it to fill in my distribution plots.

```{r}
#convert bedrooms column to Factor data type
homes$bedroom_count <- as.factor(homes$bedrooms)

```

The "homes" dataset now has a new Factor data-type variable called 
"bedroom_count". This should allow me to use the "fill" functions when creating
grouped distribution plots.

Let's get some visuals about the ages of homes.

```{r}
#plot histogram of all the ages of homes
ggplot(data=homes, aes(x=age)) + 
  geom_histogram(binwidth = 1, col = "red", fill="white") +
  labs(title="Ages of Homes") +
  labs(x="Age") +
  labs(y="# of Homes") +
  scale_x_continuous(limits=c(0,125), breaks=seq(10, 120, 10)) + 
  geom_vline(aes(xintercept=mean(age, na.rm=T)),color="blue", 
             linetype="dashed",size=1)
  
```

The average age of the 2999 observed homes is 50, which is somewhat alarming
because that may be a sign that remodeling and repairs are inevitable for our
future home. However, the histogram looks like most of the homes fall to the
left of the average line, which indicates a higher count of newer homes. 
Our ideal home is no more than 30 years old, so let's see how many homes fall
under that criteria. 

```{r}
#find how many homes are 30 years old or youger
length(which(homes$age<=30))
length(which(homes$age>30))
length(which(homes$age<=30)) + length(which(homes$age>30))

```

Well that's not what I expected. The left tail of the histogram may contain
the largest bins and seem more dense, but the right tail actually contains 
more homes because the tail itself is wider. This is disappointing because
the chances of us finding a home that's within our desired age is less likely
and we will most likely end up having to spend more money on remodeling and 
repairs. Maybe that's not such a bad thing. As long as the home prices are 
reasonably less expensive compared to the newer homes, the difference in
price could cover the additional remodeling and repair costs. I'll explore
this idea in the next section.

```{r}
#plot histogram of all the ages of homes but now group by the number of 
#bedrooms
ggplot(homes) + 
  geom_histogram(aes(age, fill=bedroom_count), binwidth=1) + 
  scale_x_continuous(limits=c(0,125), breaks=seq(10, 120, 10)) + 
  labs(x='Age of the Home', y='Count', title='Home Ages')

```

It looks like most of the homes have between 2-4 bedrooms, which is great
because we are looking for a 2-3 bedroom home.

Now let's explore the prices of homes.

```{r}
#find range of home prices and summary of home prices
range(homes$price)
summary(homes$price)
mean(homes$price)

#plot the prices of all the homes
ggplot(data=homes, aes(x=price)) + 
  geom_histogram(col = "red", fill="white") +
  labs(title="Prices of Homes", x="Price", y="# of Homes")

#lets get a better look at this distrubution
ggplot(data=homes, aes(x=price)) + 
  geom_histogram(binwidth = 25000, col = "red", fill="white") +
  labs(title="Prices of Homes") +
  labs(x="Price") +
  labs(y="# of Homes") +
  scale_x_continuous(limits=c(0,6000000), breaks=seq(0, 6000000, 500000)) +
  geom_vline(aes(xintercept=mean(price, na.rm=T)),color="blue", 
             linetype="dashed",size=1)

```

My first plot didn't really give me much insight into the data so adjusting
the binwidth and manipulating the x-axis allowed me to see that the distrubtion
of prices is heavily right-skeweed. This is good news for me because our 
budget is between $600,000 - 650,000. 

As I did before with the age of homes, I'd like to see the distribution of
prices in relation to the number of bedrooms.

```{r}
#plot the prices of homes
ggplot(homes, aes(price, fill = bedroom_count)) +
  geom_histogram(bins = 100)

ggplot(homes, aes(price, colour = bedroom_count)) +
  geom_freqpoly(bins = 100) +
  geom_vline(aes(xintercept=mean(price, na.rm=T)),color="blue", 
             linetype="dashed",size=.5)

```

I really like the second plot because it allows me to clearly see that 
3-bedroom homes are the most available and it falls below the average home
price line of $534,326. 

Now that I've looked at the distribution of prices, one variable that is not
included in the original dataset but is highly used when determining the value
of a home, is the price per square footage. Let's create this variable.

```{r}
# create a new variable to shows how much the price per square footage is
homes$price_per_sqft <- homes$price / homes$sqft_living

```

Now that we have this variable, let's plot it.

```{r}
#plot the price per square foot of all the homes
ggplot(data=homes, aes(x=price_per_sqft)) + 
  geom_histogram(col = "red", fill="white") +
  labs(title="Price Per Square Feet", x="Price Per Sq Ft", y="# of Homes")

```

As expected, the shape of this distribution is also right-skewed just like the
price histogram. 

## Bivariate Plot Section

The main purpose of this exploration is to determine what variable has the 
most influence on the price of a home. Earlier I mentioned several different
factors. Now I will explore the relationship between a few.

### Price vs Square Feet of Living Space

```{r}
# view the relationship using scatterplot 
ggplot(aes(x = sqft_living, y = price), data = homes) +
  geom_point(color = "red", alpha = 1/10) +
  labs(title="Price vs Sqft of Living Space", x="Sqft of Living Space", 
       y="Price") + 
  stat_smooth(method = "lm", formula = y ~ x, size = 1, color = "darkblue", 
              fill="darkblue")

# view relationship using line plot
ggplot(aes(x = sqft_living, y = price), data = homes) +
  geom_line(color = "red") +
  labs(title="Price vs Sqft of Living Space", x="Sqft of Living Space", 
       y="Price") +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, color = "darkblue", 
              fill="darkblue")

# perform a correlation test and see the results
cor.test(homes$price, homes$sqft_living, method = 'pearson')

```

The relationship looks to be linear with a strong correlation coefficient
of 0.70.

### Price vs Age

```{r}
# view the relationship using scatterplot 
ggplot(aes(x = age, y = price), data = homes) +
  geom_point(color = "red", alpha = 1/10) +
  labs(title="Price vs Age", x="Age", y="Price")

# view relationship using line plot
ggplot(aes(x = age, y = price), data = homes) +
  geom_line(color = "red") +
  labs(title="Price vs Age", x="Age", y="Price") 

# perform a correlation test and see the results
cor.test(homes$price, homes$age, method = 'pearson')

```

It doesn't look like there is any linear relationship between age and price but
it was interesting to see a somewhat large concentration of homes hovering
around the average home price but span across a wide age range: 15-60 years
old. 

###Price vs Location, Based on Zip Code

```{r}
# view the relationship using scatterplot 
ggplot(aes(x = zipcode, y = price), data = homes) +
  geom_point(color = "red", alpha = 1/10) +
  labs(title="Price vs Location Zip Code", x="Zip Codes", y="Price")

# view relationship using line plot
ggplot(aes(x = zipcode, y = price), data = homes) +
  geom_line(color = "red") +
  labs(title="Price vs Zipcode", x="Zipcodes", y="Price") +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, color = "darkblue", 
              fill="darkblue")

# perform a correlation test and see the results
cor.test(homes$price, homes$zipcode, method = 'pearson')

```

Based on the results, "price" was the only variable that exhibited any sign of
correlation between itself and price.

###Average & Median Price vs Age

Next, I'd like to explore the average and median price of homes based on their
age. Before doing so, I'd like to look into what statistic would be the most
accurate to use when analyzing this type of relationship between grouped
variables. Because the homes are grouped by age, I'm afraid that the average
price of an age group with only a few samples could be distorted by outliers.

```{r}
#group the records by age
homes_by_age <- group_by(homes, age)

grouped_homes_by_age <- summarise(homes_by_age,
	avg_home_price = mean(price),
	median_home_price = median(price),
	diff_bt_avg_median = avg_home_price - median_home_price,
	n = n())

#graph the difference between the age's average and median home price
ggplot(aes(x = age, y = diff_bt_avg_median), data = grouped_homes_by_age) +
  geom_line() +
  labs(title = '# of Homes by Age', x = 'Age of the Home', y = 'Diff. B/t Avg
       Home Price & Median Price')

```

The point of analyzing the difference between the average age and median for
the age groups was to see which statistic is a better representation of the 
sample. For example, age groups that have very few occurrences and a wide
range between low and high prices, would be better off using the median rather
than the average. For example, it looks like around age 10 there is a huge
spike which represents a great difference between that age's average and 
median. 

It turns out that the highest peak in the graph belongs to homes that are 9
years old and out of 11 homes in the dataset that are of that age, there is 
one outlier that is distorting the average - a $5,350,000 home. For this
reason, we will use the median price rather than the average price when 
analyzing the relationship between the prices of grouped variables. 

Now that we've came to that conclusion, let's look at the relationships.

```{r}
#graph the average price by year and median price by year
ggplot(data=grouped_homes_by_age) + 
  geom_line(aes(x = age, y = avg_home_price, colour = "Average")) + 
  geom_line(aes(x = age, y = median_home_price, colour = "Median")) +
  labs(colour = "Stats", x='Age of the Home', y='Price', 
       title='Average vs Median Price')

ggplot(data=grouped_homes_by_age, aes(x = age, y = avg_home_price)) + 
  geom_line() +
  labs(x='Age of the Home', y='Price', title='Average Home Price by Age') +
  stat_smooth(method = "loess", formula = y ~ x, size = 1, color = "darkblue", 
              fill="darkblue")

ggplot(data=grouped_homes_by_age, aes(x = age, y = median_home_price)) + 
  geom_line() +
  labs(x='Age of the Home', y='Price', title='Median Home Price by Age') +
  stat_smooth(method = "loess", formula = y ~ x, size = 1, color = "darkblue", 
              fill="darkblue")


```

Based on our previous observation of "Price vs Age" and how the result was
non-linear, I expected the average and median prices of the grouped ages to 
resemble a similar pattern. Interestingly, when I added the smoothed layer to
each individual graph, the shape of the curve almost resembled an inverted
bell-shape. Why is this occuring? One theory could be that the newer homes have
a higher value because they're just that - they are newer. And the older homes
have a higher value because they could be considered "historic" and/or since
they are so old, have since undergone a major remodel, thus increasing the 
home's value. The dip in the curve could represent those homes that are stuck
in the middle, where they aren't considered quite new anymore but are still not
old enough to warrant a full remodel. Let's see if I can find out how many 
homes between the ages of 70 - 120 have been remodeled.

```{r}
# find how many homes were remodeled between the ages of 70-120 years old
length(which(homes$yr_renovated != 0 & homes$age > 69))
length(which(homes$age > 69))
99/680

length(which(homes$yr_renovated != 0 & homes$age < 51))
length(which(homes$age > 69))
16/680

```

Out of the 680 total homes between the ages of 70-120, 99 of them have been 
renovated or roughly 15%. Compare this to the meager 2% of homes that are 50
years old or less, my speculation could be somewhat true.

```{r}
#renoated homes that are at least 70 years old

ggplot(aes(x = age, y = price), 
       data = subset(homes, homes$yr_renovated != 0 & homes$age > 69)) + 
  geom_point()

#renovated homes that are no more than 50 years old

ggplot(aes(x = age, y = price), 
       data = subset(homes, homes$yr_renovated != 0 & homes$age < 51)) + 
  geom_point()

```

The scatterplots above clearly show that the majority of renovated homes are
of the older kind.


###Median Price vs Month Sold

Moving along, like many industries, the housing market could experience their
own seasonal affects where some periods generate more revenue than others. It
would be smart to understand what time of year is the best to buy and sell.
For that reason, I will now look at what months had the highest and lowest
home prices for the year. 

```{r}
#convert the 'date' column into a standard date format

homes$date1 <- substring(homes$date, 0, 8)

homes$date1 <- gsub("(^\\d{4})(\\d{2})(\\d{2}$)", 
                                    "\\1-\\2-\\3", homes$date1)

homes$date1 <- format(as.Date(homes$date1), "%Y-%m")

#test out formating of dates

test <- '2014-10-13'

test2 <- months(as.Date(test))

test3 <- format(as.Date(test), "%Y-%m")


```


```{r}
#group the records by month
homes_by_month <- group_by(homes, date1)

grouped_homes_by_month <- summarise(homes_by_month,
	median_home_price = median(price),
	n = n())

#graph the median home price by month
ggplot(data=grouped_homes_by_month, aes(x = date1, y = median_home_price, 
                                        group = 1)) +
  geom_line(stat="identity") +
  geom_point(shape=16, size=2, fill="red", colour="blue", stroke=1) +
  labs(x='Date', y='Median Price', title='Median Home Price by Date')
  #stat_smooth(method = "loess", formula = y ~ x, size = 1, color = "darkblue", fill="darkblue")


```

Based on the graph, there is an upward trend from April to May of 2015 which 
could be an indication that home prices rise during the summer because the same
trend can be seen in the prior year. This conclusion is still inconclusive
because we don't have enough date for prior or future years.

###Homes on a Map

Now that I've explored the relationship between date & price, age & price, and
size & price, I will now look into the relationship between location and price.

```{r}
#map out the location of the homes
ggplot(aes(x=long, y=lat), data=homes) +
    geom_point()

map <- map_data("state")

ggplot(data=map) +
  geom_polygon(aes(x=long, y=lat, group = group),colour="white", 
               fill="grey10")

washington <- subset(map, region %in% c("washington"))

ggplot(data=washington) +
  geom_polygon(aes(x=long, y=lat, group = group),colour="white", 
      fill="grey10") + geom_jitter(data=homes, aes(x=long, y=lat), 
      size = 1/10, color="yellow") + scale_size(name="Home Location")

washington_zoom <- subset(map, (long > -124 & long < -119) & 
                            (lat > 46 & lat < 49))

ggplot(data=washington_zoom) +
  geom_polygon(aes(x=long, y=lat, group = group),colour="white", 
        fill="grey10") +   
  geom_point(data=homes, aes(x=long, y=lat, colour = price)) + scale_colour_gradient(low="yellow", high="red")

```

Even when switching color scales, the result still is an overwhelming majority
of yellow because most of the homes have a price less than $1 million dollars.

## Multivariate Plots Section

In this section I will add an additional layer to the various "price"
relationship graphs that I previously created. 

### Price vs Sqft of Living Space Grouped by Bedroom Count

```{r}
# prce vs sqft_living grouped by bedroom count
ggplot(homes, aes(x=sqft_living, y=price, colour = bedroom_count)) +
  geom_line() +
  labs(colour = "Bedroom Count", title = "Price vs Sqft by # of Bedrooms",
       x = "Sqft of Living", y = "Price")

ggplot(homes, aes(sqft_living, price)) +
  geom_point(color = "red") +
  facet_wrap(~bedrooms) +
  labs(x = "Sqft of Living", y = "Price", title = "Price vs Sqft Living 
       Grouped by Bedroom Count")

```

As someone looking to start a family and grow into a house, the number of
bedrooms is an important aspect to keep in mind. In our situation, we are 
planning to have 2-3 children so choosing between a 3 and 4 bedroom house is a 
big decision to make. But after looking at the results of the two plots, the
decision might not be that hard. The plots for 3 and 4 bedrooms look almost 
identical. This tells me that the number of bedrooms does not have an affect
on the price of the home, rather the square footage and size of the home is 
once again the biggest factor on price. A 2000 sqft 3-bedroom home could easily
be the exact same price as a 2000 sqft 4-bedroom home. The difference could 
simply come down to how the square footage is divided. Does one home allocate
more living space to bedrooms, hence sacrificing community and bathroom space? 
Does the other home do the opposite and create smaller rooms but increase the
size of living rooms and bathrooms? It's hard to say based off the information
provided. 

### A Look Into Activity by Month

```{r}
ggplot(aes(x=bedroom_count,y=price),data=homes)+
  geom_point(aes(colour=sqft_living))+facet_wrap(~date1)+
  scale_colour_gradientn(colours=rainbow(4)) + 
  labs(x = "# of Bedrooms", y = "Price", colour = "Sqft Living", 
  title = "Price of Homes Based on # of Bedrooms & Size, Grouped by Month")

```

In an earlier observation when I looked at median home prices by month, this 
breakdown shows the price variance for each month in terms of size and number 
of bedrooms. What's interesting about these results is the somewhat bell-shaped
curve that the distribution plots create, where the top of the curve represents
the most expensive homes which fall in the 4-bedroom group. 


#Final Plots and Summary

###Plot One

```{r}
#plot both graphs at the same time
  #newer plot
renovated_homes <- ggplot() + 
  geom_point(data = subset(homes, homes$yr_renovated != 0 & homes$age < 51), 
  aes(x = age, y = price), color = "blue") + 
  geom_smooth(data = subset(homes, homes$yr_renovated != 0 & homes$age < 51),
  aes(x = age, y = price), method = "loess") +
  #older plot
  geom_point(data = subset(homes, homes$yr_renovated != 0 & homes$age > 69), 
  aes(x = age, y = price), color = "red") + 
  labs(title="Prices of Renovated Homes", x="Age", y="Price") +
  geom_smooth(data = subset(homes, homes$yr_renovated != 0 & homes$age > 69), 
  aes(x = age, y = price), method="loess") 

renovated_homes

```

One of the most interesting discoveries I made during the exploration was the 
effect that remodeling a home could have on the price. I segmented the dataset
into two groups - a lower half containing newer homes between the ages of 1-50
and an upper half containing older homes between the ages of 70-120. When both
scatterplots are graphed simultaneously, you can see there's much 
more variance in price with the newer homes and there's a much higher frequency 
in the group of older homes. This makes sense. Older homes typically would need
additional repairs or new fixtures throughout the home to increase the value 
and make it easier to sell in the future. What's interesting about this graph
is that there's 5 homes listed above $2 million - 4 of those homes being of the
older type and 1 of them being a newer home. There's only 30 homes in the 
entire dataset that are worth more than $2 million and if 4 of the 30 are older
renovated homes, that accounts for 13%. This finding is promising for me during
my house hunt because now I understand that newer homes aren't necessarily the
only way to build equity. Yes, they certainly will save money on home repairs
and remodeling and reduce the stress of renovation, but if I can find an older
home for a good deal, I know that I can invest in renovatiations that will 
ultimately increase the value of my home.

###Plot Two

```{r}
#graph the median home price by month
ggplot(data=grouped_homes_by_month, aes(x = date1, y = median_home_price, 
                                        group = 1)) +
  geom_line(stat="identity") +
  geom_point(shape=16, size=1, fill="red", colour="blue", stroke=1) +
  geom_text(aes(x=date1, label=median_home_price), size=4, vjust=1, hjust=.5) +
  labs(x='Date', y='Median Price', title='Median Home Price by Date') +
  geom_smooth(method = "lm", colour="red", linetype="dashed")

```

I chose this graph because as a future home owner it is important to understand
trends in the housing market, that way you can predict when the best time to 
sell your home will be. If May, June, and July show upward trends in price 
compared to the rest of the year, I can do further research into what factors 
could be contributing to this. Maybe there's an increase in families looking to 
move before the new school year starts for their kids which causes the demand 
in the market to increase and swings the selling leverage over to homeowners. 
If this ends up being true, it would be beneficial to me to put more emphasis
on where my future home is located in proximity to great schools. 


###Plot Three

```{r}

bedroom_names <- c(
                    '1' = "1-Bedroom",
                    '2' = "2-Bedrooms",
                    '3' = "3-Bedrooms",
                    '4' = "4-Bedrooms",
                    '5' = "5-Bedrooms",
                    '6' = "6-Bedrooms",
                    '7' = "7-Bedrooms",
                    '8' = "8-Bedrooms"
                    )

# price vs sqft_living grouped by bedroom count
ggplot(homes, aes(sqft_living, price)) +
  geom_point(color = "red", alpha = 1/4) +
  facet_wrap(~bedrooms, labeller = as_labeller(bedroom_names)) + 
  geom_smooth(method = "lm", colour="blue") +
  labs(x = "Sqft of Living Space", y = "Price", 
  title = "Price vs Sqft Living Grouped by Bedroom Count") 

```

I chose this as my last plot of interest because at the end of my exploration,
I concluded that the biggest inflencing factor on home price was living square
footage and this graph further clarifies that notion. No matter the number of
bedrooms a house offers, the living square footage will still have the highest
correlation to an increasing price compared to all other variables. 

All in all, if I needed to make a choice as to what home to buy, I would choose
a 4-bedroom home anywhere in the range of zipcodes and if the age of the home
is on the higher end of the scale, I would make sure that it was recently 
renovated within the last 20 years. If I ever decided to sell this home, I 
would do it during the summertime, as I would get the most value out of my 
property. 

#Reflection

After working with univariate, bivariate, and multivariate plots, I feel that
each had it's own benefits. It's probably meant to be this way, but I found
myself creating a univariate plot based off of one idea, but then that quickly
segued into another question that needed to be explored using a bivariate plot,
and then that quickly became a multivariate plot. It reminded me of creating 
layers to a photoshopped image - eventually the final graphic would display a 
well detailed picture. 

I definitely need more practice but overall I feel that I have improved my 
visualization skills. The most difficult or tricky part I faced  was figuring 
out if I should work within or outside of an aesthetic. After many trial-
and-error attempts, I eventually would figure it out. Speaking of figuring 
things out, I was happy that I figured out how to account for outliers which 
helped me decide on using the median rather than the average during some of the
exploration. 

In the future, I would like to explore the idea of extrapolating the data for 
the plots where I grouped them by Month. The dataset only contained values for
one year but if I truly wanted to create a more precise model of what the 
best time of year to sell a home would be, I would need to include data for 
many years. Earlier I touched on the notion of schools potentially playing a
factor in home prices, so I would also like to explore that avenue and possibly
import data related to schools.
